DaLi: Database as a Library

### 2017-02-20 paper/motivation.tex
DaLi counter added.

>>>>

\name lets programmers add replication and persistence to their
applications without having to re-engineer their abstractions or
reason about lower-level artifacts. Here is how you write a mergeable
counter in \name:
\begin{figure}[!h]
  \begin{ocaml}
    module Counter = struct
      include Counter
      type mergeable_t = t [@@deriving persistence]
      let merge old v1 v2 = old + (v1 - old) + (v2 - old)
    end
  \end{ocaml}
\end{figure}
